---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggframe

*{ggframe}* is a *{ggplot2}* wrapper. A "ggframe" object is a data.frame with
a "layers" and an "aes" attributes. It has a printing method which plots
by default, but print with `plot = FALSE` and you'll print the data, aesthetics
and layers.

You cannot do all you can do with *{ggplot2}*, it's just an exploration of some
ideas. Unlikely to go much further.

Some nice things that you can do more easily than in native *{ggplot2}* : 

* data wrangling on plot data (assuming you use functions that don't drop attributes, 
it seems *{dplyr}* functions don't, base R functions often do)
* keep track of the steps that built the plot.

## Installation

Install with:

``` r
remotes::install_github("moodymudskipper/ggframe")
```
## Functions

`map_aes()` sets an `aes` attribute.

`geom()`, `facet()`, `set_labs`, `set_coord()`, `set_theme()`, `set_scale()` 
and `set_guide()` are quick and dirty wrappers that
add the relevant plot building call to the `layer` attribute, 
I suppose a more serious version of the package would provide a wrapper for all
relevant *{ggplot2}* functions, with explicit arguments rather than just `...`. 
One advantage here is that it works with other packages extending *{ggplot2}*.

`as_ggplot()` converts a ggframe object to a standard ggplot object.

## Examples

```{r}
library(dplyr, warn.conflicts = FALSE)
library(ggplot2) # needs to be attached, geoms etc can come from other packages too
library(ggframe)

# fast to type for a quick plot 
iris %>%
  geom("point", aes(Petal.Length, Petal.Width, color = Species)) 

# defining default aes
iris %>%
  map_aes(Petal.Length, Petal.Width, color = Species) %>%
  geom("point") 

# wrangle the data after the layer definitions
iris %>%
  map_aes(Petal.Length, Petal.Width, color = Species) %>%
  geom("point") %>%
  filter(Species != "versicolor")

# print data, aesthetics and layers
iris %>%
  map_aes(Petal.Length, Petal.Width, color = Species) %>%
  geom("point") %>%
  slice_sample(n = 15) %>%
  print(plot = FALSE)

# use set_* functions to leverage other features
iris %>%
  map_aes(Petal.Length, Petal.Width, color = Species) %>%
  geom("point") %>%
  set_coord("fixed") %>%
  set_theme("classic") %>%
  set_scale("color_viridis_d") %>%
  set_labs(title = "hello")
```

In *{ggplot2}* the `ggplot()` functions takes as optional arguments the data and aesthetics
to be inherited by further layers. It doesn't link explicitly aesthetics to a datasets
(you can define aesthetics to be inherited, but use a different dataset for every layer) 
but it's quite rare to start without a default data layer nor default aesthetics.

Moreover when providing custom data for a layer, in my experience we generally don't
provide completely new data, but a transformation of the main data. Indeed the `data`
argument of geoms can be a function or formula to be applied on the main data.

It works quite nicely here:

```{r}
iris %>%
  map_aes(Petal.Length, Petal.Width) %>%
  geom("point", data = head, color = "blue") %>%
  geom("point", data = tail, color = "red")
```

Thanks to the fact that `ggplot2::ggplot_build()` is generic and called by
`layer_data()`, `layer_scales()` and `layer_grob()`, we could make those
work directly on ggframe objects :

```{r}
# leverage layer_data easily
iris %>%
  map_aes(Petal.Length, Petal.Width) %>%
  geom("point", data = head, color = "blue") %>%
  geom("point", data = tail, color = "red") %>%
  layer_data(2)
```

