---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggframe

*{ggframe}* is a *{ggplot2}* wrapper. A "ggframe" object is a data.frame with
a "layers" and an "aes" attributes. It has a printing method which prints a plot
by default.

You cannot do all you can do with *{ggplot2}*, it's just an exploration of some
ideas. Unlikely to go much further.

Some nice things that you can do more easily than in native *{ggplot2}* : 

* data wrangling on plot data (assuming you use functions that don't destroy attributes, it seems *{dplyr}* function don't, base R functions often do)
* keep track of the steps that built the plot.

## Installation

You can install the released version of ggframe from [CRAN](https://CRAN.R-project.org) with:

``` r
remotes::install_github("moodymudskipper/ggframe")
```

## Example

```{r}
library(dplyr, warn.conflicts = FALSE)
library(ggplot2) # needs to be attached, geoms etc can come from other packages too
library(ggframe)

iris %>%
  map_aes(Petal.Length, Petal.Width, color = Species) %>%
  geom("point") 

iris %>%
  map_aes(Petal.Length, Petal.Width, color = Species) %>%
  geom("point") %>%
  filter(Species != "versicolor")

iris %>%
  map_aes(Petal.Length, Petal.Width, color = Species) %>%
  geom("point") %>%
  slice_sample(n = 15) %>%
  print(plot = FALSE)


iris %>%
  map_aes(Petal.Length, Petal.Width, color = Species) %>%
  geom("point") %>%
  set_coord("fixed") %>%
  set_theme("classic") %>%
  set_scale("color_viridis_d")
```
